\documentclass{resume}
\usepackage[default]{lato}
\usepackage{hyperref}
\usepackage[left=0.4in,top=0.4in,right=0.4in,bottom=0.4in]{geometry}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

\name{William McIntosh}
\address{145 Shakespeare Road, Auckland, Auckland 0620, New Zealand}
\address{+64 7 808 0446 \\ \href{mailto:will@ahead.nz}{will@ahead.nz} \\ \href{https://ahead.nz}{ahead.nz}}

\begin{document}

\begin{rSection}{PROFESSIONAL PROFILE}
With a Master’s in Computer Science, 3 years in data science, and 10 years in people management, I’m excited for a fresh start in New Zealand. Embracing a major career change, my love for learning and high tolerance for ambiguity drive me. Drawn by the work-life balance and great environment for raising my kids, I’m eager to join the kiwi tech community, and I believe this is possible working together with you at Basis to radically accelerate the clean-energy revolution with smarter, safer, and more efficient homes. 
\end{rSection}

\begin{rSection}{MIGRATION STATUS}
My wife and I graduated from Portland State University on June 15th and are moving to Auckland on July 28th. Our immigration advisor, Charlotte Stockman from NZ Shores, has handled all paperwork and fees. We just need a job offer from an accredited employer to complete the process. charlotte@nzshores.com, 07 929 2280.
\end{rSection}

\begin{rSection}{EDUCATION}
\textbf{Master's of Science in Computer Science} \hfill {2023 - 2024} \\
Portland State University

\textbf{Bachelor's of Science in Data Science} \hfill {2018 - 2023} \\
Portland State University, \textit{summa cum laude}
\end{rSection}

\begin{rSection}{EXPERIENCE RELEVANT TO SOFTWARE MODELS AND DATA ANALYST INTERN}
\textbf{Data Scientist at Homeoptions, Inc.} \hfill 2021 - 2023 \\
\begin{itemize}
    \item Designed predictive modeling and machine learning algorithms, showcasing capabilities aligned with Basis' emphasis on building software models, data analysis, and cloud services. Developed advanced proficiency in AWS similar to cloud infrastructure like GCP.
    \item Crafted a sophisticated predictive model utilizing logistic regression and XGBoost for accurate binary classification, demonstrating a strong foundation in data science frameworks akin to Python Pandas - a skill desired by Basis.
    \item Fostered innovative cloud architecture and service deployment strategies using AWS API Gateway and Lambda, reflecting Basis' need for optimally managing and executing software in the cloud environment.
\end{itemize}

\textbf{Computer Science Tutor at Portland State University} \hfill 2020 - 2021 \\
\begin{itemize}
    \item Innovated teaching methods using Unity and C# to elucidate complex concepts, demonstrating proficiency in software languages like C and C++, as required by Basis for the Internship role.
    \item Assisted in shaping computer science curriculum, reflecting Basis' requirement for an understanding of the wider system beyond software, and the ability to articulate system impacts on software.
\end{itemize}

\textbf{Graduate Research Assistant at Portland State University} \hfill 2023 - 2024 \\
\begin{itemize}
    \item Utilized Python to automate data collection and cleaning - foundational skills that connect with Basis' job scope in probabilistic methods and implementing robust data quality checks.
    \item Implemented Python's copy\_from method to rapidly upload records into a PostgreSQL database, demonstrating experience with data storage and management, which are essential for prototyping and data analysis tasks described by Basis.
\end{itemize}
\end{rSection}

\begin{rSection}{VOLUNTEER EXPERIENCE}
\textbf{Computer Science Peer Mentor} \hfill 2020 - 2021 \\
We In Computer Science --- Portland State University \\
\begin{itemize}
    \item Directed mentorship programs and event coordination within the computer science department, demonstrating strong leadership and organization skills, which reflect Basis' core values of innovation and collaboration.
    \item Built and fostered a supportive learning community, directly aligning with Basis' pursuit of creating impactful experiences and understanding human behavior.
\end{itemize}

\textbf{Youth Mentor} \hfill 2018 - 2019 \\
Big Brothers Big Sisters Columbia Northwest --- Portland, Or. USA \\
\begin{itemize}
    \item Provided transformative mentorship, fostering personal and academic growth, which speaks to Basis' commitment to professional development and supporting learning.
    \item Engaged with the community to promote the mentoring program, underscoring communication and interpersonal skills that are valuable for cross-functional collaboration, a relevant aspect of working with engineers at Basis.
\end{itemize}
\end{rSection}

\begin{rSection}{WORK EXPERIENCE TIMELINE}
\textbf{Data Scientist} \hfill 2021 - 2023 \\
Homeoptions, Inc. --- Remote

\textbf{Customer Support Manager} \hfill 2017 - 2018 \\
Procore, Inc. --- Portland, Or. USA

\textbf{Graduate Research Assistant} \hfill 2023 - 2024 \\
Port of Portland, PDX Airport --- Portland, Or. USA
\end{rSection}

\end{document}